---
title: "R Notebook"
output: RNN model
---
carregando bibliotecas

```{r}
library("rattle")
library("dplyr")
library("rnn")
library("ggplot2")
```

Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Ctrl+Alt+I*.

Carregando dados
```{r}
data <- read.csv("db_balanco_temp_geracao.csv")

#Inverter a ordem das ações para pegar da última para a ´primeira
data <-data[order(data$data, decreasing = TRUE),]


```

Criando dataset com os dados temporais da carga
```{r}
carga <- data$mean

carga_anterior <- lead(carga,n=1L)

data_analise <- data.frame(carga)
data_analise$carga_anterior <- carga_anterior


summary(data_analise)
```
Tratando os dados
```{r}

#exclui NA
data_analise = na.omit(data_analise)
data_analise <- subset(data_analise, !rowSums(data_analise == 0))
data_used <- data_analise[1:1100,]

summary(data_used)

x <- data_used[,2]
y <- data_used[,1]


X <- matrix(x, nrow = 100)
Y <- matrix(y, nrow = 100)


Yscaled <- (Y - min(Y)) / (max(Y) - min(Y))
Xscaled <- (X - min(X)) / (max(X) - min(X))
Y <- Yscaled
X <- Xscaled
```

Separando o treino e teste
```{r}
train=1:8
test=9:11

set.seed(12)
model <- trainr(Y = Y[,train],
                X = X[,train],
                learningrate = 0.05,
                hidden_dim = 20,
                numepochs = 500,
                network_type = "rnn"
                )


#no conjunto de treinamento
Ytrain <- t(matrix(predictr(model, X[,train]),nrow=1))
Yreal <- t(matrix(Y[,train],nrow=1))
```
Plot graph de erros

```{r}
model$error
#poucas épocas?
plot(colMeans(model$error),type='l',xlab='epoch',ylab='errors')
```

Plot graph para treino

```{r}
#Percentual de variação em uma variável explicada por outra
rsq <- function(y_actual,y_predict){
  cor(y_actual,y_predict)^2
}

rsq(Yreal,Ytrain)

plot(Ytrain, type = "l", col = "darkred",
     main = "Actual vs trained load: training set",
     ylab = "Y,Ytrain")
lines(Yreal, col = "darkblue", type = "l")
legend("bottomright", c("Treino", "Atual"),
col = c("red","black"),
lty = c(1,1), lwd = c(1,1))

```
Testando modelo
```{r}
#no conjunto de teste
Ytest=matrix(Y[,test], nrow = 1)
Ytest = t(Ytest)
Yp <- predictr(model, Y[,test])
Ypredicted=matrix(Yp, nrow = 1)
Ypredicted=t(Ypredicted)

result_data <- data.frame(Ytest)
result_data$Ypredicted <- Ypredicted     

rsq(result_data$Ytest, result_data$Ypredicted)

mean(result_data$Ytest)
mean(result_data$Ypredicted)
```


Plot graph teste 
```{r}
plot(as.vector(t(result_data$Ytest)), col = 'red', type='l',
main = "Actual vs Predicted load: testing set",
ylab = "Y,Yp")
lines(as.vector(t(Yp)), type = 'l', col = 'black')
legend("bottomright", c("Predicted", "Actual"),
col = c("red","black"),
lty = c(1,1), lwd = c(1,1))
```



When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Ctrl+Shift+K* to preview the HTML file).

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.
